---
title       : Building Data Product Assignment #2
subtitle    : Forecast sales data using Linear Regression.
author      : Suresh Joshi
job         : Data Engineer
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides

---

## Introduction
This presentation is produced using slidfy app. In this project I am using synthetic sale data.
The data set consists of yearly sales of 4 ficticious companies (named Company 1, Company 2, Company 3 and Company 4).
We fit the linear regression model using year and company as covariate and sales as response variable.

```{r  echo=FALSE, results='hide'}
library(shiny)
library(ggplot2)
library(xtable)

sales_data <- data.frame(
  year = rep(c(2010,2011,2012,2013,2014,2015), 4),
  company = c(rep(c('company1'), 6), 
              rep(c('company2'), 6), 
              rep(c('company3'), 6), 
              rep(c('company4'), 6)),
  sales = c(
    c(366 ,756 ,2554 ,4504 ,3106 ,2348),
    c(1982 ,7637 ,17098 ,14399 ,17890 ,18785),
    c(26 ,26 ,100 ,241 ,323 ,241),
    c(50 ,59 ,130 ,206 ,250 ,204)
  )
)
```

---
## Data Summary
```{r} 
str(sales_data)
summary(sales_data)
```
```{r echo=FALSE, results='hide'}
gen_data <- function(start_year, end_year, companies) {
  #generate data for year bewteen start_year and end_year
  year <- c()
  company <- c()
  count <- length(companies)
  for (y in start_year:end_year) {
    year <-	c(year, c(rep(y,count)))
    company <- c(company, companies)
  }
  data.frame(year = year, company = company)
}

g <- ggplot(sales_data, aes(x = round(year,0), y = log(sales), color = company, size = 10)) +
  geom_point(size = 7) + theme_bw(base_family = "Times", base_size = 12) + 
  labs(y="log(Sales)", x="Year", size=5 ) + 
  theme(axis.text=element_text(size=15),axis.title=element_text(size=15,face="bold"))
    new_data <-
      gen_data(2016, 2020, c('company1','company2','company3','company4'))
    new_data$sales <- stats::predict(model, new_data)
    #geom_line(data = new_data,size = 1, linetype =3)
```

--- .class #id 
## Linear Regression Model

```{r}
model <- glm(sales ~ year * factor(company), data = sales_data)
```    
```{r results="asis", echo=FALSE}
xt <- xtable(summary(model))
print(xt, type="html")
```


--- .class #id 

## Plot of sales data.

Note: dotted line indicates predicted data.
```{r echo=FALSE, fig.align='left', fig.width=13}
g +  geom_line(size = 2) + geom_point(data = new_data, size = 5, shape =8)

```    




